Docker as a Development Environment for Research Papers

### 2020-11-18 ms.tex
{make test} remove QMNIST and EMNIST to fit in github action runner
change name of project

\title{Reproducible Builds for\\ Computational Research Papers}

@@

We propose a template for writing computational research papers with \LaTeX\ and verifying  its reproducibility using the concept of \textit{reproducible builds} (RBs) in a local or remote computational environment.
We provide an open source implementation of the template\footnote{\url{https://github.com/pbizopoulos/cookiecutter-reproducible-builds-for-computational-research-papers}}, which we use to write this paper\footnote{\url{https://arxiv.org/abs/2005.12660}} and verify its reproducibility\footnote{\url{https://github.com/pbizopoulos/reproducible-builds-for-computational-research-papers}}.
We use Python~\cite{van2007python} for producing the results, however other scientific-oriented programming languages can be used.

@@

\section{Example Use Case of RBs}
This sections provides a use case of RBs and also serves as a manual for creating reproducible \textit{papers} written in \LaTeX\ with Python as the \textit{results code} programming language.
For demonstration purposes we train and test a VGG11 neural network~\cite{simonyan2014very} with batch normalization in PyTorch~\cite{paszke2019pytorch}, on the following datasets:
\begin{itemize}
	\item MNIST~\cite{lecun2010mnist},
	\item FashionMNIST~\cite{xiao2017fashion},
	\item KMNIST~\cite{clanuwat2018deep},
	\item QMNIST~\cite{yadav2019cold},
	\item EMNIST~\cite{cohen2017emnist},
	\item CIFAR10~\cite{krizhevsky2009learning},
	\item CIFAR100~\cite{krizhevsky2009learning} and
	\item SVHN~\cite{netzer2011reading}.
\end{itemize}

>>>>

\title{Docker as a Development Environment for Research Papers}

@@

We propose a template for writing computational research papers with \LaTeX\ and verifying  its reproducibility using the concept of \textit{reproducible builds} (RBs) in a local or remote computational environment.
We provide an open source implementation of the template\footnote{\url{https://github.com/pbizopoulos/docker-as-a-development-environment-for-research-papers-template}}, which we use to write this paper\footnote{\url{https://arxiv.org/abs/2005.12660}} and verify its reproducibility\footnote{\url{https://github.com/pbizopoulos/docker-as-a-development-environment-for-research-papers}}.
We use Python~\cite{van2007python} for producing the results, however other scientific-oriented programming languages can be used.

@@

\section{Example Use Case of RBs}
This sections provides a use case of RBs and also serves as a manual for creating reproducible \textit{papers} written in \LaTeX\ with Python as the \textit{results code} programming language.
For demonstration purposes we train and test a VGG11 neural network~\cite{simonyan2014very} with batch normalization in PyTorch~\cite{paszke2019pytorch}, on the following datasets:
\begin{itemize}
	\item MNIST~\cite{lecun2010mnist},
	\item FashionMNIST~\cite{xiao2017fashion},
	\item KMNIST~\cite{clanuwat2018deep},
	\item CIFAR10~\cite{krizhevsky2009learning},
	\item CIFAR100~\cite{krizhevsky2009learning} and
	\item SVHN~\cite{netzer2011reading}.
\end{itemize}
